---
title: "Chinook salmon consumption by Steller sea lions along the northwest coast of Washington"
author: "Zoë K. Lewis and Dr. Benjamin Nelson"
date: "2022-08-12"
output: 
 html_document:
    toc: true
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    code_folding: show
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Description

Biomass of Chinook salmon consumed by Steller sea lions between December 2020-August 2021 along the northwest coast of Washington.Daily prey consumption models for Steller sea lions adapted from Scordino et al. 2022 "Dietary niche overlap and prey consumption estimates for Steller sea lion and California sea lion in northwest Washington, 2010-2013". Fishery Bulletin.

## Required packages

```{r echo = T, results = 'hide'}
library(ANOVAreplication)
library(dplyr)
library(colorspace)
library(viridis)
library(zoib)
library(ggplot2)
library(lemon)

##ZOIB determined juvenile proportions
juvprop <- read.csv("/Users/zoeklewis/Desktop/juv_diet_prop_samples.csv", header=TRUE, stringsAsFactors = FALSE)

```


## Percentage of diet Chinook 

Individual consumption varies and also depends on proportions, and was modeled using using ZOIB to acount for the zero-inflation of these data. 


### Modeling set-up 

## Calculating individual salmon consumption per day 

To compare with previous findings in Chasco et al. 2017 table 6, our first step is to calculate the number of Chinook salmon consumed per day within a given season. 

Equation 1: $$ D = I*C / (W*(1/1000))$$
where;

* D = Number of Chinook salmon consumed by individual per day 
* I = Individual Daily Consumption of a demographic group in kg/day (see IndDailyConsumption)
* C = percentage of diet Chinook (depending on age class)
* W = weight of Chinook individual (g)

## Individual Daily Consumption 

### Percentage of body weight consumed

Percent body weight consumed based on body weight estimates and sex are the same as those used in "Dietary niche overlap and prey consumption estimates for Steller sea lion and California sea lion in northwest Washington 2010-2013" (Scordino et al. 2020) derived from Winship et al. 2006. Percent body weight consumed determined using either normal distribution or uniform distributions. 

```{r}
#Female P 
FLarge <- rnorm(1,0.05,0.01)
FMed <- runif(1,0.06,0.07)
FMedSm <- runif(1,0.07,0.08)
FSmall <- runif(1,0.08,0.09)

#Male P 
MLarge <- runif(1,0.03,0.04)
MMed <- rnorm(1,0.04,0.01)
MMedSm <- runif(1,0.05,0.06)
MSmall <- runif(1,0.06,0.07)
MVSmall <- runif(1,0.08,0.09)
```

### Daily consumption of prey (kg/day) by demographic 

"Formulas for estimating the daily consumption of a randomly drawn juvenile female juvenile male, adult female, and adult male using the consumption of body weight parameters defined above and the uniform distribution of reported weight at age for each age and sex class as reported in Winship et al. 2001. Juvenile weights are for sea lions ages 1 to 5. Juvenile females use non-pregnant 5 year old weight as the maximum weight for the category. Adults use age classes of 5 up to maximum growth from Winship et al. 2001." - Scordino et al. 2020 

```{r}

## Individual daily consumption juvenile female (I)
IndDailyConsumptionJuvF<- function() 
{
  JuvF <- runif(1,89,195)
  if(JuvF > 194){JuvF*FMed}
  if(JuvF > 152){JuvF*FMedSm}
  if(JuvF > 89){JuvF*FSmall}
}

## Individual daily consumption adult female (I)
IndDailyConsumptionAdF<- function() 
{
  AdFemale <- runif(1,195,305)
  if(AdFemale > 223){AdFemale*FLarge}
  if(AdFemale > 195){AdFemale*FMed}
}

## Individual daily consumption juvenile male (I)
IndDailyConsumptionJuvM<- function() 
{
  JuvM <- runif(1,125,286)
  if(JuvM > 182){JuvM*MSmall}
  if(JuvM > 125){JuvM*MVSmall}
}

## Individual daily consumption adult male (I)
IndDailyConsumptionAdM<- function() 
{
  AdMale <- runif(1,286,681)
  if(AdMale > 623){AdMale*MLarge}
  if(AdMale > 455){AdMale*MMed}
  if(AdMale > 310){AdMale*MMedSm}
  if(AdMale > 286) {AdMale*MSmall}
}
```



## Weight of Chinook by age class

Weight of Chinook individual will vary on age class of salmon. 
Lengths determined from length-age information in Chasco et al. 2017.

```{r, echo=FALSE, results='asis'}
library(knitr)

agelength <- read.csv("/Users/zoeklewis/Documents/WWU/Biomass Model Manuscript /Working model code/length-age.csv")

kable(agelength, caption = "Length (mm) - Age (years) Relationships for Chinook salmon on the outer northwest coast of Washington State Chasco et al. 2017")

```

Length weight relationship determined by allometric equation for Chinook salmon where;

Equation 2: $$ W = (a*(L/10)^b)/1000 $$

* W = weight of Chinook salmon (g)
* a = 9.61
* L = length of Chinook salmon (mm)
* b = 3.07

### Allometric functions for monthly weight of Age-0 juveniles

```{r}

DecJuvChinWt <- function()
  {
  (9.61*((rlnorm(1, log(236.9987), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}
DecJuvChinWt()

JanJuvChinWt <- function()
  {
  (9.61*((rlnorm(1, log(175.436), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

FebJuvChinWt <- function()
  {
  (9.61*((rlnorm(1, log(170.2746), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

MarJuvChinWt <- function()
  {
  (9.61*((rlnorm(1, log(201.9993), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

AprJuvChinWt <- function()
  {
  (9.61*((rlnorm(1, log(234.8554), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

MayJuvChinWt <- function()
  {
  (9.61*((rlnorm(1, log(173.6663), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

JunJuvChinWt <- function()
  {
  (9.61*((rlnorm(1, log(142.0207), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

JulJuvChinWt <- function()
  {
  (9.61*((rlnorm(1, log(133.1082), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}

AugJuvChinWt <- function()
  {
  (9.61*((rlnorm(1, log(151.4996), sdlog = 0.5))/10)^3.07)*(1/1000)*(1/1000)
}
```


## Individual Daily consumption (Age 0 Chinook salmon/day) by demographic and season {.tabset}
Back to the initially described equation; 
$$ D = I*C / (W*(1/1000))$$

### Juvenile Female Steller sea lion consumption of Age 0 salmon 
Monthly time-step for Chinook length/weight
Seasonal time-step for ZOIB estimates
 
``` {r}
DecIndJuvFdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvF())/DecJuvChinWt())) * juvprop$winter_samples
DecIJFD <- quantile(DecIndJuvFdailysal0, probs = c(0.5, 0.025, 0.975))

JanIndJuvFdailysal0 <- replicate(n=10000, ((IndDailyConsumptionJuvF())/JanJuvChinWt())) * juvprop$winter_samples
JanIJFD <- quantile(JanIndJuvFdailysal0, probs = c(0.5, 0.025, 0.975))

FebIndJuvFdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvF())/FebJuvChinWt())) * juvprop$winter_samples
FebIJFD <- quantile(FebIndJuvFdailysal0, probs = c(0.5, 0.025, 0.975))

MarIndJuvFdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvF())/MarJuvChinWt())) * juvprop$spring_samples
MarIJFD <- quantile(MarIndJuvFdailysal0, probs = c(0.5, 0.025, 0.975))

AprIndJuvFdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvF())/AprJuvChinWt())) * juvprop$spring_samples
AprIJFD <- quantile(AprIndJuvFdailysal0, probs = c(0.5, 0.025, 0.975))

MayIndJuvFdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvF())/MayJuvChinWt())) * juvprop$spring_samples
MayIJFD <- quantile(MayIndJuvFdailysal0, probs = c(0.5, 0.025, 0.975))

JuneIndJuvFdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvF())/JunJuvChinWt())) * juvprop$summer_samples
JuneIJFD <- quantile(JuneIndJuvFdailysal0, probs = c(0.5, 0.025, 0.975))

JulyIndJuvFdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvF())/JulJuvChinWt())) * juvprop$summer_samples
JulyIJFD <- quantile(JulyIndJuvFdailysal0, probs = c(0.5, 0.025, 0.975))

AugIndJuvFdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvF())/AugJuvChinWt())) * juvprop$summer_samples
AugIJFD <- quantile(AugIndJuvFdailysal0, probs = c(0.5, 0.025, 0.975))

JuvFemaleconsumption <- cbind(DecIJFD, JanIJFD, FebIJFD, MarIJFD, AprIJFD, MayIJFD, JuneIJFD, JulyIJFD, AugIJFD)

```


### Juvenile Male Steller sea lion consumption of Age 0 salmon 
Monthly time-step for Chinook length/weight
Seasonal time-step for ZOIB estimates
 
``` {r}
DecIndJuvMdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvM())/DecJuvChinWt())) * juvprop$winter_samples
DecIJMD <- quantile(DecIndJuvMdailysal0, probs = c(0.5, 0.025, 0.975))

JanIndJuvMdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvM())/JanJuvChinWt()))* juvprop$winter_samples
JanIJMD <- quantile(JanIndJuvMdailysal0, probs = c(0.5, 0.025, 0.975))

FebIndJuvMdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvM())/FebJuvChinWt()))* juvprop$winter_samples
FebIJMD <- quantile(FebIndJuvMdailysal0, probs = c(0.5, 0.025, 0.975))

MarIndJuvMdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvM())/MarJuvChinWt()))* juvprop$spring_samples
MarIJMD <- quantile(MarIndJuvMdailysal0, probs = c(0.5, 0.025, 0.975))

AprIndJuvMdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvM())/AprJuvChinWt()))* juvprop$spring_samples
AprIJMD <- quantile(AprIndJuvMdailysal0, probs = c(0.5, 0.025, 0.975))

MayIndJuvMdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvM())/MayJuvChinWt()))* juvprop$spring_samples
MayIJMD <- quantile(MayIndJuvMdailysal0, probs = c(0.5, 0.025, 0.975))

JuneIndJuvMdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvM())/JunJuvChinWt())) * juvprop$summer_samples
JuneIJMD <- quantile(JuneIndJuvMdailysal0, probs = c(0.5, 0.025, 0.975))

JulyIndJuvMdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvM())/JulJuvChinWt())) * juvprop$summer_samples
JulyIJMD <- quantile(JulyIndJuvMdailysal0, probs = c(0.5, 0.025, 0.975))

AugIndJuvMdailysal0 <- replicate(n=10000,((IndDailyConsumptionJuvM())/AugJuvChinWt())) * juvprop$summer_samples
AugIJMD <- quantile(AugIndJuvMdailysal0, probs = c(0.5, 0.025, 0.975))

JuvMaleconsumption <- cbind(DecIJMD, JanIJMD, FebIJMD, MarIJMD, AprIJMD, MayIJMD, JuneIJMD, JulyIJMD, AugIJMD)
```

### Adult female Steller sea lion consumption of Age 0 salmon 
Monthly time-step for Chinook length/weight
Seasonal time-step for ZOIB estimates
 
``` {r}
DecIndAdFdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdF())/DecJuvChinWt()))* juvprop$winter_samples
DecIAFD <- quantile(DecIndAdFdailysal0, probs = c(0.5, 0.025, 0.975))

JanIndAdFdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdF())/JanJuvChinWt()))* juvprop$winter_samples
JanIAFD <- quantile(JanIndAdFdailysal0, probs = c(0.5, 0.025, 0.975))

FebIndAdFdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdF())/FebJuvChinWt()))* juvprop$winter_samples
FebIAFD <- quantile(FebIndAdFdailysal0, probs = c(0.5, 0.025, 0.975))

MarIndAdFdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdF())/MarJuvChinWt()))* juvprop$spring_samples
MarIAFD <- quantile(MarIndAdFdailysal0, probs = c(0.5, 0.025, 0.975))

AprIndAdFdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdF())/AprJuvChinWt()))* juvprop$spring_samples
AprIAFD <- quantile(AprIndAdFdailysal0, probs = c(0.5, 0.025, 0.975))

MayIndAdFdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdF())/MayJuvChinWt()))* juvprop$spring_samples
MayIAFD <- quantile(MayIndAdFdailysal0, probs = c(0.5, 0.025, 0.975))

JuneIndAdFdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdF())/JunJuvChinWt()))* juvprop$summer_samples
JuneIAFD <- quantile(JuneIndAdFdailysal0, probs = c(0.5, 0.025, 0.975))

JulyIndAdFdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdF())/JulJuvChinWt()))* juvprop$summer_samples
JulyIAFD <- quantile(JulyIndAdFdailysal0, probs = c(0.5, 0.025, 0.975))

AugIndAdFdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdF())/AugJuvChinWt()))* juvprop$summer_samples
AugIAFD <- quantile(AugIndAdFdailysal0, probs = c(0.5, 0.025, 0.975))

AdultFemaleconsumption <- cbind(DecIAFD, JanIAFD, FebIAFD, MarIAFD, AprIAFD, MayIAFD, JuneIAFD, JulyIAFD, AugIAFD)

```

### Adult male Steller sea lion consumption of Age 0 salmon 

``` {r}
DecIndAdMdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdM())/DecJuvChinWt()))* juvprop$winter_samples
DecIAMD <- quantile(DecIndAdMdailysal0, probs = c(0.5, 0.025, 0.975))

JanIndAdMdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdM())/JanJuvChinWt()))* juvprop$winter_samples
JanIAMD <- quantile(JanIndAdMdailysal0, probs = c(0.5, 0.025, 0.975))

FebIndAdMdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdM())/FebJuvChinWt()))* juvprop$winter_samples
FebIAMD <- quantile(FebIndAdMdailysal0, probs = c(0.5, 0.025, 0.975))

MarIndAdMdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdM())/MarJuvChinWt()))* juvprop$spring_samples
MarIAMD <- quantile(MarIndAdMdailysal0, probs = c(0.5, 0.025, 0.975))

AprIndAdMdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdM())/AprJuvChinWt()))* juvprop$spring_samples
AprIAMD <- quantile(AprIndAdMdailysal0, probs = c(0.5, 0.025, 0.975))

MayIndAdMdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdM())/MayJuvChinWt()))* juvprop$spring_samples
MayIAMD <- quantile(MayIndAdMdailysal0, probs = c(0.5, 0.025, 0.975))

JuneIndAdMdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdM())/JunJuvChinWt()))* juvprop$summer_samples
JuneIAMD <- quantile(JuneIndAdMdailysal0, probs = c(0.5, 0.025, 0.975))

JulyIndAdMdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdM())/JulJuvChinWt()))* juvprop$summer_samples
JulyIAMD <- quantile(JulyIndAdMdailysal0, probs = c(0.5, 0.025, 0.975))

AugIndAdMdailysal0 <- replicate(n=10000,((IndDailyConsumptionAdM())/AugJuvChinWt()))* juvprop$summer_samples
AugIAMD <- quantile(AugIndAdMdailysal0, probs = c(0.5, 0.025, 0.975))


AdultMaleconsumption <- cbind(DecIAMD, JanIAMD, FebIAMD, MarIAMD, AprIAMD, MayIAMD, JuneIAMD, JulyIAMD, AugIAMD)
```


### Overall daily consumption table 

```{r}
individual_daily <- cbind(JuvFemaleconsumption, JuvMaleconsumption, AdultFemaleconsumption, AdultMaleconsumption)
```

## Total Steller sea lion consumption

### Abundance Estimates

Counts are from surveys conducted from 2020-2021 data counts only. I only included surveys that
had all haulouts surveyed in that day. For a few surveys I pulled East Bodelteh counts into a 
day that otherwise had an incomplete count. Raw data for the counts are available from Scordino and Akmajian 2021.

```{r, echo=FALSE, results='asis'}

abundance <- read.csv("/Users/zoeklewis/Documents/WWU/Biomass Model Manuscript /Working model code/abundance.csv")

kable(abundance, caption = "Negative binomial parameters to estimate total Non-pups by season")

```

Abundance formulas are as follows: 

```{r}

#Winter Steller sea lion abundance
WinAbund <- function()
  {
  rnbinom(n=1, mu=1029.12735, size=25.47853)
}

SprAbund <- function()
  {
  rnbinom(n=1, mu=1023.0994, size=14.97663)
}

SumAbund <- function()
{
  rnbinom(n=1, mu=1122.51676, size=27.45719)
}
```

Count correction factors: 

Correction factors from Olesiuk 2018 were used assuming that the correction factor for fall and spring have the same CF as caculated for winter. This assumption is supported by the findings of Whitlock et al. 2020 of very low attendance in May and by the end of August that were similar to Olesiuk's estimate for winter CF. Overall the correction factors from Olesiuk 2018 were similar to the estimates of Whitlock et al. 2020. These correction  factors were for Steller sea lions. Olesiuk found that 36% of non-pups (SD=2.1%) were hauled out in fall, winter, and spring during the time window of 10:00 - 18:00 when our counts typically occurred. During summer Olesiuk found that 67.4% of non-pups (SD= 5.6%) were hauled out during survey time periods. Note that Olesiuk (2018) errored in reporting that 2.1% was the winter CV and 5.6% was the summer CV of the proportion of population hauled out; both should have read SD instead of CV (Personal communication Peter Olesiuk, 2021).

```{r}
WinSprFallCF <- function()
{
  1/(rnorm(1,0.36,0.021))
  }

SummerCF <- function()
{
  1/rnorm(1,0.674,0.056)
  }

```

### Determining seasonal demographic with beta distribution {.tabset}

Count data from Scordino and Akmajian (2021) were used to determine the proportion of the hauled out Steller sea lions that were adult male, adult female, and juvenile.I have used the excel file 'SSFO pRey Table and Abundance Parameters for Modeling'
sheet 'EJ Seasonal 2010-2013' to calculate mean and standard deviation of total non-pup counts. This calculation used more surveys than did the calculations, usign the same excel file and sheet, for %male, %female, and %juvenile as I was able to use counts that did not have demographics for all haulouts surveyed within a day.

Season	  Avg F Sd F  Avg J Sd J  Avg M Sd M  n
Spring 	0.379	0.099	0.426	0.098	0.195	0.071 11
Summer 	0.261	0.055	0.408	0.055	0.330	0.071 9
Winter 	0.390	0.104	0.406	0.046	0.205	0.074 4

The proportions of individuals hauled out of each demographic group is best modeled using a beta distribution. To calculate the beta distribution we first calculated the shape 1 and shape 2 of the distribution for each demographic group by season.

#### Winter

```{r}
##Observed demographic proportions 
Mean_winter_j = 0.406 #Juvenile avg
sd_winter_j = 0.046 #Juvenile sd
Mean_winter_f = 0.390 #Female avg 
sd_winter_f = 0.104 #Female sd
Mean_winter_m = 0.205 #Male avg 
sd_winter_m = 0.074 #Male sd 


## Beta distribution shapes 
### Juvenile 
Winter_j_shape1 <- (Mean_winter_j^2-Mean_winter_j^3-Mean_winter_j*sd_winter_j^2)/sd_winter_j^2
Winter_j_shape2 <- (Mean_winter_j-2*Mean_winter_j^2+Mean_winter_j^3-sd_winter_j^2+Mean_winter_j*sd_winter_j^2)/sd_winter_j^2
### Adult female
Winter_f_shape1 <- (Mean_winter_f^2-Mean_winter_f^3-Mean_winter_f*sd_winter_f^2)/sd_winter_f^2
Winter_f_shape2 <- (Mean_winter_f-2*Mean_winter_f^2+Mean_winter_f^3-sd_winter_f^2+Mean_winter_f*sd_winter_f^2)/sd_winter_f^2
### Adult male
Winter_m_shape1 <- (Mean_winter_m^2-Mean_winter_m^3-Mean_winter_m*sd_winter_m^2)/sd_winter_m^2
Winter_m_shape2 <- (Mean_winter_m-2*Mean_winter_m^2+Mean_winter_m^3-sd_winter_m^2+Mean_winter_m*sd_winter_m^2)/sd_winter_m^2

### Beta distribution functions for demographics 

WinJuvDemo <- function()
{
  rbeta(n=1,shape1=Winter_j_shape1,shape2=Winter_j_shape2)
}
WinFemDemo <- function()
{
  rbeta(n=1,shape1=Winter_f_shape1,shape2=Winter_f_shape2)
}
WinMaleDemo <- function()
{
  rbeta(n=1,shape1=Winter_m_shape1,shape2=Winter_m_shape2)
}
```

#### Spring

```{r}
##Observed demographic proportions 
Mean_spring_j = 0.426
sd_spring_j = 0.098
Mean_spring_f = 0.379
sd_spring_f = 0.099
Mean_spring_m = 0.195
sd_spring_m = 0.071

#@# Beta distribution shapes 
### Juvenile 
Spring_j_shape1 <- (Mean_spring_j^2-Mean_spring_j^3-Mean_spring_j*sd_spring_j^2)/sd_spring_j^2
Spring_j_shape2 <- (Mean_spring_j-2*Mean_spring_j^2+Mean_spring_j^3-sd_spring_j^2+Mean_spring_j*sd_spring_j^2)/sd_spring_j^2
### Adult Female
Spring_f_shape1 <- (Mean_spring_f^2-Mean_spring_f^3-Mean_spring_f*sd_spring_f^2)/sd_spring_f^2
Spring_f_shape2 <- (Mean_spring_f-2*Mean_spring_f^2+Mean_spring_f^3-sd_spring_f^2+Mean_spring_f*sd_spring_f^2)/sd_spring_f^2
### Adult male
Spring_m_shape1 <- (Mean_spring_m^2-Mean_spring_m^3-Mean_spring_m*sd_spring_m^2)/sd_spring_m^2
Spring_m_shape2 <- (Mean_spring_m-2*Mean_spring_m^2+Mean_spring_m^3-sd_spring_m^2+Mean_spring_m*sd_spring_m^2)/sd_spring_m^2

### Beta distribution functions for demographics 

SprJuvDemo <- function()
{
rbeta(n=1,shape1=Spring_j_shape1,shape2=Spring_j_shape2)
}
SprFemDemo <- function()
{
rbeta(n=1,shape1=Spring_f_shape1,shape2=Spring_f_shape2)
}
SprMaleDemo <- function()
{
rbeta(n=1,shape1=Spring_m_shape1,shape2=Spring_m_shape2)
}
```

#### Summer

```{r}
Mean_summer_j = 0.408
sd_summer_j = 0.055
Mean_summer_f = 0.261
sd_summer_f = 0.055
Mean_summer_m = 0.330
sd_summer_m = 0.071

#@# Beta distribution shapes 
### Juvenile 
summer_j_shape1 <- (Mean_summer_j^2-Mean_summer_j^3-Mean_summer_j*sd_summer_j^2)/sd_summer_j^2
summer_j_shape2 <- (Mean_summer_j-2*Mean_summer_j^2+Mean_summer_j^3-sd_summer_j^2+Mean_summer_j*sd_summer_j^2)/sd_summer_j^2
### female
summer_f_shape1 <- (Mean_summer_f^2-Mean_summer_f^3-Mean_summer_f*sd_summer_f^2)/sd_summer_f^2
summer_f_shape2 <- (Mean_summer_f-2*Mean_summer_f^2+Mean_summer_f^3-sd_summer_f^2+Mean_summer_f*sd_summer_f^2)/sd_summer_f^2
### male
summer_m_shape1 <- (Mean_summer_m^2-Mean_summer_m^3-Mean_summer_m*sd_summer_m^2)/sd_summer_m^2
summer_m_shape2 <- (Mean_summer_m-2*Mean_summer_m^2+Mean_summer_m^3-sd_summer_m^2+Mean_summer_m*sd_summer_m^2)/sd_summer_m^2

### Beta distribution functions for demographics 

SumJuvDemo <- function()
{
rbeta(n=1,shape1=summer_j_shape1,shape2=summer_j_shape2)
}
SumFemDemo <- function()
{
rbeta(n=1,shape1=summer_f_shape1,shape2=summer_f_shape2)
}
SumMaleDemo <- function()
{
rbeta(n=1,shape1=summer_m_shape1,shape2=summer_m_shape2)
}
```

### Correction factors for demographic proportions 

"I used data from supplemental table 2 from Wright et al. 2017 to calculate
expected ratio of females to males for juvenile Steller sea lions rather than assuming a 50:50 sex ratio. I used data for cohorts from 2001 through 2007 since they all had survival rates through age 5. I then averaged the survivorship at age for age 1 through age 5 for each cohort by sex and used the ratio of the two to inform what percent of juveniles were female and male." 

The proportion of Juvenile sex are as follows: 

```{r}

PropJuvF <- 0.544
PropJuvM <- 0.456
```


## Overall consumption - Total fish consumed by Steller sea lions on the northwest Washington Coast {.tabset}

The final formula to calculate consumption for each season was split into four parts: 
juvenile female, juvenile male, adult female, and adult male.

Within each demographic group the formula was (abundance of non-pups*proportion of demographic
group * number of days in the season * count correction factor
*the estimate of daily consumption of the demographic group (kg). 


For juveniles an added factor multiplied by the estimated proportion of juveniles for each sex, respectively.

### Winter consumption of Age 0 Fish 

```{r}

EjWinterJuvF <-
  (replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvF*(31)*((IndDailyConsumptionJuvF())/DecJuvChinWt()))* juvprop$winter_samples) + 
  (replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvF*(31)*((IndDailyConsumptionJuvF())/JanJuvChinWt()))* juvprop$winter_samples) + 
  (replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvF*(28)*((IndDailyConsumptionJuvF())/FebJuvChinWt()))* juvprop$winter_samples) 

WinJuvF <- quantile(EjWinterJuvF,probs = c(0.5, 0.025, 0.975))
WinJuvF

EjWinterJuvM <-
  replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvM*(31)*((IndDailyConsumptionJuvM())/DecJuvChinWt())) * juvprop$winter_samples  + 
  replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvM*(31)*((IndDailyConsumptionJuvM())/JanJuvChinWt())) * juvprop$winter_samples + 
  replicate(n=10000, WinAbund()* WinSprFallCF()*WinJuvDemo()*PropJuvM*(28)*((IndDailyConsumptionJuvM())/FebJuvChinWt()))* juvprop$winter_samples 

WinJuvM <- quantile(EjWinterJuvM,probs = c(0.5, 0.025, 0.975))
WinJuvM

EjWinterAdF <-
  replicate(n=10000, WinAbund()* WinSprFallCF()*WinFemDemo()*(31)*((IndDailyConsumptionAdF())/DecJuvChinWt())) * juvprop$winter_samples  + 
  replicate(n=10000, WinAbund()* WinSprFallCF()*WinFemDemo()*(31)*((IndDailyConsumptionAdF())/JanJuvChinWt())) * juvprop$winter_samples  + 
  replicate(n=10000, WinAbund()* WinSprFallCF()*WinFemDemo()*(28)*((IndDailyConsumptionAdF())/FebJuvChinWt())) * juvprop$winter_samples 

WinAdF <- quantile(EjWinterAdF,probs = c(0.5, 0.025, 0.975))
WinAdF

EjWinterAdM <-
  replicate(n=10000, WinAbund()* WinSprFallCF()*WinMaleDemo()*(31)*((IndDailyConsumptionAdF())/DecJuvChinWt())) * juvprop$winter_samples   + 
  replicate(n=10000, WinAbund()* WinSprFallCF()*WinMaleDemo()*(31)*((IndDailyConsumptionAdF())/JanJuvChinWt())) * juvprop$winter_samples + 
  replicate(n=10000, WinAbund()* WinSprFallCF()*WinMaleDemo()*(28)*((IndDailyConsumptionAdF())/FebJuvChinWt()))* juvprop$winter_samples 

WinAdM <- quantile(EjWinterAdM,probs = c(0.5, 0.025, 0.975))
WinAdM

Winter <- EjWinterJuvF + EjWinterJuvM + EjWinterAdF + EjWinterAdM

WinterTot <- quantile(Winter,probs = c(0.5, 0.025, 0.975))
WinterTot

```

### Spring consumption of Age 0 Fish 
```{r}

EjSpringJuvF <-
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvF*(31)*((IndDailyConsumptionJuvF())/MarJuvChinWt())) * juvprop$spring_samples  + 
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvF*(31)*((IndDailyConsumptionJuvF())/AprJuvChinWt()))* juvprop$spring_samples  + 
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvF*(28)*((IndDailyConsumptionJuvF())/MayJuvChinWt()))* juvprop$spring_samples 

SprJuvF <- quantile(EjSpringJuvF, probs = c(0.5, 0.025, 0.975))


EjSpringJuvM <-
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvM*(31)*((IndDailyConsumptionJuvM())/MarJuvChinWt())) * juvprop$spring_samples  + 
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvM*(31)*((IndDailyConsumptionJuvM())/AprJuvChinWt()))* juvprop$spring_samples  + 
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprJuvDemo()*PropJuvM*(28)*((IndDailyConsumptionJuvM())/MayJuvChinWt()))* juvprop$spring_samples 

SprJuvM <- quantile(EjSpringJuvM, probs = c(0.5, 0.025, 0.975))

EjSpringAdF <-
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprFemDemo()*(31)*((IndDailyConsumptionAdF())/MarJuvChinWt()))* juvprop$spring_samples   + 
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprFemDemo()*(31)*((IndDailyConsumptionAdF())/AprJuvChinWt())) * juvprop$spring_samples + 
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprFemDemo()*(28)*((IndDailyConsumptionAdF())/MayJuvChinWt()))* juvprop$spring_samples 

SprAdF <- quantile(EjSpringAdF, probs = c(0.5, 0.025, 0.975))

EjSpringAdM <-
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprMaleDemo()*(31)*((IndDailyConsumptionAdF())/MarJuvChinWt())) * juvprop$spring_samples  + 
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprMaleDemo()*(31)*((IndDailyConsumptionAdF())/AprJuvChinWt()))* juvprop$spring_samples  + 
  replicate(n=10000, SprAbund()* WinSprFallCF()*SprMaleDemo()*(28)*((IndDailyConsumptionAdF())/MayJuvChinWt()))* juvprop$spring_samples 

SprAdM <- quantile(EjSpringAdF, probs = c(0.5, 0.025, 0.975))

Spring <- EjSpringJuvF + EjSpringJuvM + EjSpringAdF + EjSpringAdM

SpringTot <- quantile(Spring,probs = c(0.5, 0.025, 0.975))
SpringTot
```

### Summer consumption of Age 0 Fish 

```{r}
EjSummerJuvF <-
  replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvF*(31)*((IndDailyConsumptionJuvF())/JunJuvChinWt())) * juvprop$summer_samples + 
  replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvF*(31)*((IndDailyConsumptionJuvF())/JulJuvChinWt()))* juvprop$summer_samples  + 
  replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvF*(28)*((IndDailyConsumptionJuvF())/AugJuvChinWt()))* juvprop$summer_samples 

SumJuvF <- quantile(EjSummerJuvF, probs = c(0.5, 0.025, 0.975))

EjSummerJuvM <-
  replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvM*(31)*((IndDailyConsumptionJuvM())/JunJuvChinWt())) * juvprop$summer_samples  + 
  replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvM*(31)*((IndDailyConsumptionJuvM())/JulJuvChinWt()))* juvprop$summer_samples  + 
  replicate(n=10000, SumAbund()* SummerCF()*SumJuvDemo()*PropJuvM*(28)*((IndDailyConsumptionJuvM())/AugJuvChinWt()))* juvprop$summer_samples 

SumJuvM <- quantile(EjSummerJuvM, probs = c(0.5, 0.025, 0.975))

EjSummerAdF <-
  replicate(n=10000, SumAbund()* SummerCF()*SumFemDemo()*(31)*((IndDailyConsumptionAdF())/JunJuvChinWt())) * juvprop$summer_samples  + 
  replicate(n=10000, SumAbund()* SummerCF()*SumFemDemo()*(31)*((IndDailyConsumptionAdF())/JulJuvChinWt()))* juvprop$summer_samples  + 
  replicate(n=10000, SumAbund()* SummerCF()*SumFemDemo()*(28)*((IndDailyConsumptionAdF())/AugJuvChinWt()))* juvprop$summer_samples 

SumAdF <- quantile(EjSummerAdF, probs = c(0.5, 0.025, 0.975))

EjSummerAdM <-
  replicate(n=10000, SumAbund()* SummerCF()*SumMaleDemo()*(31)*((IndDailyConsumptionAdF())/JunJuvChinWt())) * juvprop$summer_samples  + 
  replicate(n=10000, SumAbund()* SummerCF()*SumMaleDemo()*(31)*((IndDailyConsumptionAdF())/JulJuvChinWt())) * juvprop$summer_samples + 
  replicate(n=10000, SumAbund()* SummerCF()*SumMaleDemo()*(28)*((IndDailyConsumptionAdF())/AugJuvChinWt()))* juvprop$summer_samples 

SumAdM <- quantile(EjSummerAdM, probs = c(0.5, 0.025, 0.975))

Summer <- EjSummerJuvF + EjSummerJuvM + EjSummerAdF + EjSummerAdM

SummerTot <- quantile(Summer,probs = c(0.5, 0.025, 0.975))
SummerTot
```
